---
title: "SmallChange"
author: "Team Play With Impact - Alexandra Titova, Cindy Russell, David Lim, Lachlan Jensen"
date: "2023-08-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## From little things, big things grow.

Children grow up fast.

And as they do, they outgrow clothes, shoes, equipment and toys.

Small Change is here to help give your pre-loved goods a new lease on life.

```{r cars}
summary(cars)
```

## Track your impact

Understanding the impact of a program is essential to determine its impact. Tracking a secondhand item throughout its lifecycle as it moves from person to person can generate important data and assist in creating a positive future for the program.

We track that impact using blockchain technology through our SmallChange tokens.  Blockchain can keep a record of the history of each donated item. This allows us to track the movement of the item through its life item and helps us create data sets based on age of child/ren, location, how long the item was used for, and can even help to connect communities and share stories through these shared goods. 

Tracking items usage also ensures that items do reach their intended recipient. This helps create transparency within the charity and allows charities to remain genuine and trustworthy in the eyes of the donors and the general public. 

Additionally, tracking items helps donors feel like they are personally helping and involved in the donation process. Many individuals have emotional connections to preloved items and they want to know that their items are still being used and appreciated. And if we find a strong match between donors and recipients, it’s likely that their future unwanted goods can find a second life.

Allowing donors to watch their item move through its lifecycle also builds a relationship between the donor and the charity. This makes the donor more likely to donate their items in the future through the same charity and prevent more items from entering landfill. 

Lastly, tracking also allows us to identify areas where individuals need more support. According to RemoteOpShop.org, about 15% out of Australia’s 22 million population live in rural and remote areas. Individuals in these areas are more likely to need affordable second-hand items and are less likely to donate items due to the lack of accessibility and availability of charity stores. 

By tracking items and their impact, we can see which areas are receiving needed items and which areas may be being left behind. Additionally, we can see which specific items are in-high demand in specific areas and ensure that when items are donated, we can prioritise those locations.   


```{r pressure, echo=FALSE}
plot(pressure)
```

## Giving where it matters

We have analysed data from the census and combined it with other geography-based measures of socio-economic status to match the impact of your donations to where it counts.

As more people use SmallChange, our algorithms will improve to match profiles.

